Semantic Linearity in a Lazy Optimising Compiler

### 2024-02-12 icfp.tex
typos

\renewcommand{\LinearDeltaRelationLemma}{
  \begin{restatable}[Linear to $\Delta$-bound]{lemma}{onedelta}\label{lem:onedelta}
If $\G; \D',\xl \vdash e :\vp$
then $\G[\D/x],\xD; \D,\D' \vdash e : \vp$, with fresh $\D$.
\end{restatable}
}

@@

\paragraph{$\Delta$-bound variables} Our development relies on the following characterization of $\D$-bound
variables:
A well-typed program with a linear variable ($\xl$) is equivalently
well-typed if the linear variable were instead $\D$-bound ($\xD$) with
usage environment $\D$, with $\D$

available in the linear context instead of
the linear variable (and the unrestricted context updated accordingly).
\LinearDeltaRelationLemma

>>>>

\renewcommand{\LinearDeltaRelationLemma}{
  \begin{restatable}[Linear to $\Delta$-bound]{lemma}{onedelta}\label{lem:onedelta}
If $\G; \D',\xl \vdash e :\vp$
then $\G[\D/x],\xD; \D,\D' \vdash e : \vp$ ($\Delta$ fresh).
\end{restatable}
}

@@

\paragraph{$\Delta$-bound variables} Our development relies on the following characterization of $\D$-bound
variables:
A well-typed program with a linear variable ($\xl$) is equivalently
well-typed if the linear variable were instead $\D$-bound ($\xD$) with
usage environment $\D$, with $\D$ available in the linear context (and the unrestricted context updated accordingly).

\LinearDeltaRelationLemma
